The Chemistry Development Kit (CDK). 3. Atom typing, Rendering, Molecular Formula, and Substructure Searching

### 2013-10-17 article.tex
Updated my affiliation detail
Wrote a bit of the introduction

\author{
  Egon L Willighagen$^{1}$% // FIXED FIRST AUTHOR
  \email{Egon L Willighagen - COMPLETE}
\and
  John May$^2$% // FIXED SECOND AUTHOR
  \email{John May - COMPLETE@ebi.ac.uk}
\and
  Jonathan Alversson$^3$%
  \email{Jonathan Alversson - COMPLETE}
\and
  Arvid Berg$^3$%
  \email{Arvid Berg - COMPLETE}
\and
  Nina Jeliazkova$^4$%
  \email{Nina Jeliakvova - COMPLETE}
\and
  Dazhi Jiao$^5$%
  \email{Dazhi Jiao - COMPLETE}
\and
  Syed Asad Rahman$^6$%
  \email{Syed Asad Rahman - COMPLETE}
\and
  Mark Rijnbeek$^2$%
  \email{Mark Rijnbeek - COMPLETE}
\and
  Miguel Rojas Cherto$^7$%
  \email{Miguel Rojas Cherto - COMPLETE}
\and
  Ola Spjuth$^3$%
  \email{Ola Spjuth - ola.spjuth@farmbio.uu.se}
\and
  Gilleain Torrance$^5$%
  \email{Gilleain Torrance - COMPLETE}
\and
  Rajarshi Guha$^{8}$% // FIXED ONE BUT LAST AUTHOR
  \email{Rajarshi Guha - COMPLETE}
\and
  Christoph Steinbeck$^{2}$% // FIXED LAST AUTHOR
  \email{Christoph Steinbeck - steinbeck@ebi.ac.uk}
}

\address{
    \iid(1)Department of Bioinformatics - BiGCaT, \\
    \iid(2)Chemoinformatics and Metabolism team, European Bioinformatics Institute, Hinxton, UK, \\
    \iid(3)Department of Pharmaceutical Biosciences, Uppsala University, 751 24 Uppsala, Sweden \\
    \iid(4)Ideaconsult Ltd, A. Kanchev 4, Sofia 1000, Bulgaria \\
    \iid(5)Example Ltd., Glasgow, UK \\
    \iid(6)Example Ltd., Glasgow, UK \\
    \iid(7)Division of Analytical Biosciences, Leiden/Amsterdam Center for Drug Research, Leiden, The Netherlands \\
    \iid(8)NIH Center for Translational Therapeutics, 9800 Medical Center Drive, Rockville, MD 20878, USA
}

@@

Open Source cheminformatics state \ldots (EGON)

Adoption of the CDK ... Cinfony~\cite{OBoyle2008}, and other bindings \ldots ...

Recent prominent use cases of the CDK~\cite{Steinbeck2003,Steinbeck2006} \ldots (EGON)
AMBIT~\cite{jeliazkova2011ambit}, jCompoundMapper~\cite{Hinselmann2011},
ScaffoldHunter~\cite{wetzel2009interactive}, OMG~\cite{Peironcely2012}, Padel~\cite{yap2011padel}, ...

Plugins for Taverna\cite{Truszkowski2011}, KNIME\cite{Beisken2013}, ...

Some extensions make it back into the main library, like SMSD~\cite{} and fingerprints from Padel.
Not all extensions made it back into the main library, such as those from
AMBIT-SMARTS~\cite{jeliazkova2011ambitsmarts}, AMBIT-Tautomer~\cite{kochev2013ambit}, FooFromRydberg~\cite{}.

>>>>

\author{
  Egon L Willighagen$^{1}$% // FIXED FIRST AUTHOR
  \email{Egon L Willighagen - egon.willighagen@maastrichtuniversity.nl}
\and
  John May$^2$% // FIXED SECOND AUTHOR
  \email{John May - COMPLETE@ebi.ac.uk}
\and
  Jonathan Alversson$^3$%
  \email{Jonathan Alversson - COMPLETE}
\and
  Arvid Berg$^3$%
  \email{Arvid Berg - COMPLETE}
\and
  Nina Jeliazkova$^4$%
  \email{Nina Jeliakvova - COMPLETE}
\and
  Dazhi Jiao$^5$%
  \email{Dazhi Jiao - COMPLETE}
\and
  Syed Asad Rahman$^6$%
  \email{Syed Asad Rahman - COMPLETE}
\and
  Mark Rijnbeek$^2$%
  \email{Mark Rijnbeek - COMPLETE}
\and
  Miguel Rojas Cherto$^7$%
  \email{Miguel Rojas Cherto - COMPLETE}
\and
  Ola Spjuth$^3$%
  \email{Ola Spjuth - ola.spjuth@farmbio.uu.se}
\and
  Gilleain Torrance$^5$%
  \email{Gilleain Torrance - COMPLETE}
\and
  Rajarshi Guha$^{8}$% // FIXED ONE BUT LAST AUTHOR
  \email{Rajarshi Guha - COMPLETE}
\and
  Christoph Steinbeck$^{2}$% // FIXED LAST AUTHOR
  \email{Christoph Steinbeck - steinbeck@ebi.ac.uk}
}

\address{
    \iid(1)Department of Bioinformatics - BiGCaT, Maastricht University, Maastricht, NL-6200 MD, The Netherlands \\
    \iid(2)Chemoinformatics and Metabolism team, European Bioinformatics Institute, Hinxton, UK, \\
    \iid(3)Department of Pharmaceutical Biosciences, Uppsala University, 751 24 Uppsala, Sweden \\
    \iid(4)Ideaconsult Ltd, A. Kanchev 4, Sofia 1000, Bulgaria \\
    \iid(5)Example Ltd., Glasgow, UK \\
    \iid(6)Example Ltd., Glasgow, UK \\
    \iid(7)Division of Analytical Biosciences, Leiden/Amsterdam Center for Drug Research, Leiden, The Netherlands \\
    \iid(8)NIH Center for Translational Therapeutics, 9800 Medical Center Drive, Rockville, MD 20878, USA
}

@@

Open Source cheminformatics has made significants steps recently~\cite{OBoyle2011}.
Development of the Chemistry Development Kit (CDK) has been previously documented~\cite{Steinbeck2003,Steinbeck2006},
but followed this general trend in open source cheminformatics, and increased in functionality
and adoption. For example, new tools expose CDK functionality, such as Cinfony~\cite{OBoyle2008},
rcdk~\cite{}, and workflow plugins for Taverna\cite{Truszkowski2011}, KNIME\cite{Beisken2013}.
Furthermore, projects with specific functionality have emerged building on the CDK, including
jCompoundMapper~\cite{Hinselmann2011}, ScaffoldHunter~\cite{wetzel2009interactive}, OMG~\cite{Peironcely2012},
Padel~\cite{yap2011padel}, AMBIT-SMARTS~\cite{jeliazkova2011ambitsmarts}, AMBIT-Tautomer~\cite{kochev2013ambit},
SMSD~\cite{}, and FooFromRydberg~\cite{}. Other tools used previous versions already, and follow
newer releases of the CDK, such as Bioclipse~\cite{} and AMBIT~\cite{jeliazkova2011ambit}.

Importantly, the CDK has seen independent validation ... of both functionality, quality, and performance...
... fingerprint results ... performance paper ... Sayle MDL atom type work.
